---
title: "Homework - 1"
author: "Krishna Ramachandra(24200269) "
format: pdf
editor: visual
---

```{r}
#| echo: false
#Loading the Dataset
data(mtcars)
```

### Sample of the MtCars dataset

```{r}
#| echo: false
#Displaying the first 5 rows of the dataset
head(mtcars)
```

#### ***Description:***

*The mtcars dataset comprises fuel consumption and 10 aspects of automobile design and performance for 32 car models from the 1973–74 Motor Trend magazine.*

*Each row corresponds to a different car model, and each column is a numeric attribute related to that car.*

### **Summary**

```{r}
#| echo: false
#Displaying the statistics of 3 columns of the dataset
summary(mtcars[, c("mpg", "wt", "cyl")])
```

### **Scatter Plot**

```{r}
#| echo: false
#Importing the library
library(ggplot2)

# Creating the scatter plot
ggplot(mtcars, aes(x = wt, y = mpg, color = as.factor(cyl))) +
  geom_point(size = 3) +
  #Setting the title and name of the axis for the plot
  labs(
    title = "Scatter Plot of Fuel Efficiency vs. Car Weight",
    subtitle = "Grouped by Number of Cylinders",
    x = "Weight (1000 lbs)",
    y = "Miles Per Gallon (mpg)",
    color = "Cylinders"
  ) +
  theme_minimal()

```

-   **Negative correlation**:

    There is a **clear downward trend**, showing that **as weight increases, fuel efficiency decreases**. Heavier cars tend to consume more fuel.

<!-- -->

-   **Cylinders as a differentiator**:

```         
-    4-cylinder cars (red) are generally lighter and more fuel-efficient.

-    6-cylinder cars (green) are in the middle range for both weight and mpg.

-    8-cylinder cars (blue) are heavier and less fuel-efficient.
```

## Homework - 2

#### Commit - 1

```{r}
# Plotting a histogram of miles per gallon
hist(mtcars$mpg,
     main = "Histogram of Miles Per Gallon (mpg)",
     xlab = "Miles Per Gallon",
     col = "lightblue",
     border = "black")

```

#### Commit - 2

```{r}
# Boxplot of mpg by number of cylinders
boxplot(mpg ~ cyl,
        data = mtcars,
        main = "MPG by Number of Cylinders",
        xlab = "Number of Cylinders",
        ylab = "Miles Per Gallon (mpg)",
        col = c("orange", "lightblue", "lightgreen"))

```
